30 years of privacy research for the masses \& \newline 15 years of decentralization attempts

### 2014-03-13 paper.tex
Add section labels used in the introduction

	\section{Tor vulnerabilities and attacks}
		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.

@@

	\section{Problems when decentralizing}
		As we saw in the previous section, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

@@

	\section{Current decentralized systems}
		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@

	\section{Comparison existing decentralized  networks}
		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@

	\section{Conclusion}
		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network. Furthermore we looked at the main disadvantages and problems Tor currently has. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. The next section shows which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.

>>>>

	\section{Tor vulnerabilities and attacks}
		\label{sec:attacks}

		Besides the disadvantages mentioned in the previous section, Tor also suffers from several vulnerabilities that can be exploited trough attacks \cite{abbott2007browser, douceur2002sybil, bauer2007low}. In this section we will summarize some of the most well known problems with Tor as well as define the following categories of attacks: Browser based attacks, Low-Resource Routing attacks, Sybil attacks and Replay attacks.

@@

	\section{Problems when decentralizing}
		\label{sec:problems}

		As we saw in the previous section, we would like to have a decentralized anonymous network. This isn't an easy task: 15 years of decentralization attempts on the Tor network are behind us. Several well-used decentralized peer-to-peer overlay networks are active such as Gnutella [link], Freenet [link] and Tapestry. These networks will be described in more detail in the next chapter. Among these networks are some overlay anonymous networks such as Tarzan.

@@

	\section{Current decentralized systems}
		\label{sec:decentralized}

		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@

	\section{Comparison existing decentralized  networks}
		\label{sec:comparison}

		Many other decentralized peer-to-peer networks have been proposed and some have been implemented [linkjes naar papers]. Examples of fully decentralized networks are Gnutella, Freenet, Freehaven, Tapestry, Kademlia and Tarzan. Each of these decentralized networks will be discussed in the next section. Note that we're only considering fully decentralized networks here. Networks that are partially or hybrid centralized, such as KaZaA and Napster, are not discussed here.[link naar survey p2p?]

@@

	\section{Conclusion}
		\label{sec:conclusion}

		In this technical report we introduced Tor and explained how Tor works and which components define a Tor network. Furthermore we looked at the main disadvantages and problems Tor currently has. We then made a bridge to decentralized systems. We first explained which problems one might face when decentralizing a system such as Tor. The next section shows which systems currently have a decentralized structure and/or mechanism. These systems are then compared to each other with their pros and cons.
